---
title: "DS Final Project"
author: "Neha Anand, John Morkos, Zach Murphy, Thomas Le"
date: "5/18/2021"
output:  flexdashboard::flex_dashboard
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading data, echo=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(plotly)
library(datasets)
library(shinyWidgets)
vaccines = read_csv("https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/us_state_vaccinations.csv")

cases = read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv")

cases_clean = cases %>% pivot_longer(names_to="Date", values_to="Cases", cols=colnames(cases[12:length(cases)]))
cases_clean = cases_clean %>% mutate(Date = as.Date(cases_clean$Date, format ="%m/%d/%y"))

deaths = read_csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv")
deaths_clean = deaths %>% pivot_longer(names_to="Date", values_to="Cases", cols=colnames(deaths[13:length(deaths)]))
deaths_clean = deaths_clean %>% mutate(Date = as.Date(deaths_clean$Date, format ="%m/%d/%y"))

model_dat = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Time%20Series%20Analysis/models.csv")

```

Heat Map 
======================
Sidebar {.sidebar}
----------------------------------
### Select Inputs
```{r input1, echo=FALSE, message=FALSE}
selectInput("vaccine_trend_1", "Select vaccination term", c("daily vaccinations", "daily vaccinations per million"))
selectInput("google_trends_1", "Select a google search term", c("covid", "vaccine", "vaccine near me", "mask", "social distancing", "qanon"))
selectInput("lag", "Select lag time (days)", c(3, 7, 14))
```

Heat Map {data-width=100000}
-------------------------------------
### Heat Map
```{r rendering heat map, fig_width=20, fig.height=10, fig.fulwidth=TRUE, echo=FALSE}
library(ggplot2)
library(RColorBrewer)
library(ggmap)
library(maps)
library(rgdal)
library(scales)
library(shiny)
library(maptools)
library(gridExtra)
library(rgeos)
library(rgdal)
# download.file("https://www2.census.gov/geo/tiger/TIGER2017//STATE/tl_2017_us_state.zip" , destfile="US_shape_file.zip")
# system("unzip US_shape_file.zip")
# my_spdf <- readOGR( 
#   dsn= paste0(getwd()),
#   layer="tl_2017i_us_state",
#   verbose=FALSE
# )
# 
# plot(my_spdf)
library(ggplot2)
library(RColorBrewer)
all_states<-map_data("state")
names(all_states)[names(all_states)=="region"] <- "state"
url="https://raw.githubusercontent.com/jmorkos1/DS-Project-2021/main/Time%20Series%20Analysis/models.csv"
data=read.csv("https://raw.githubusercontent.com/jmorkos1/DS-Project-2021/main/Time%20Series%20Analysis/models.csv")
clean_data=subset(data, select=-c(pvalue, f, acf_x, acf_y, res_norm_p, res_hsce_p, res_acor_p))
capFirst <- function(s) {
  paste(toupper(substring(s, 1, 1)), substring(s, 2), sep = "")
}
all_states$state <- capFirst(all_states$state)
# all_states <- all_states[all_states$state=="North dakota"=="North Dakota" | all_states$state=="South dakota"=="South Dakota" |all_states$state=="North carolina"=="North Carolina" |all_states$state=="South carolina"=="South Carolina" |all_states$state=="West virginia "=="West Virginia" |all_states$state=="New mexico"=="New Mexico"|all_states$state=="New hampshire"=="New Hampshire"|all_states$state=="New york"=="New York"|all_states$state=="New jersey"=="New Jersey"|all_states$state=="Rhode island"=="Rhode Island",]
all_states$state[all_states$state=="North dakota"] <- "North Dakota" 
all_states$state[all_states$state=="South dakota"] <- "South Dakota" 
all_states$state[all_states$state=="North carolina"] <- "North Carolina" 
all_states$state[all_states$state=="West virginia"] <- "West Virginia" 
all_states$state[all_states$state=="New mexico"] <- "New Mexico" 
all_states$state[all_states$state=="New hampshire"] <- "New Hampshire" 
all_states$state[all_states$state=="New york"] <- "New York" 
all_states$state[all_states$state=="New jersey"] <- "New Jersey" 
all_states$state[all_states$state=="Rhode island"] <- "Rhode Island" 
all_states$state[all_states$state=="South carolina"] <- "South Carolina" 
renderPlot({
  vt1 = gsub(" ", "_", as.character(input$vaccine_trend_1))
  clean_data_red <- clean_data[clean_data$outcome==(vt1) & clean_data$term==(input$google_trends_1),]
  merged_data <- merge(clean_data_red, all_states, by="state")
  merged_data$state<-factor(merged_data$state)
  final_data <- merged_data[order(merged_data$order),]
  redgreen <- c("red", "green") 
  pal <- colorRampPalette(redgreen)(100)
  p<-ggplot(final_data, aes(long, lat, group=group, fill=r2, color='red')) +
    geom_polygon(color="red") + scale_fill_gradientn(colours=rev(heat.colors(10)),na.value="grey90") 
  p
})
# renderDataTable({
# clean_data_red <- clean_data[clean_data$outcome==(input$vaccine_trend_1) & clean_data$term==(input$google_trends_1),]
# all_states$state <- capFirst(all_states$state)
# merged_data <- merge(clean_data_red, all_states, by="state")
# merged_data$state<-factor(merged_data$state)
# final_data <- merged_data[order(merged_data$order),]
# final_data
# })
```


Graphs of Trends 
======================

Sidebar {.sidebar}
---------------------------------------------
### Select Inputs

```{r input2, echo=FALSE, message=FALSE}

selectInput("vaccine_trend_2", "Select vaccination term", c("daily vaccinations",
  "daily vaccinations per million"))

selectInput("google_trends_2", "Select a google search term", c("covid", "vaccine", "vaccine near me", "mask", "social distancing", "qanon"))

awesomeCheckbox("points", "Raw data points", value=TRUE, status="info")
awesomeCheckbox("line", "Add lines", status="info")
awesomeCheckbox("smooth", "Add smoothed time series", status="info")


states = c(state.name)
pickerInput("states", "Select up to 5 states", states, selected="Alabama", multiple=TRUE, options=pickerOptions(actionsBox=TRUE, maxOptions=5, maxOptionsText="Please select 5 or less states"))
```

Column {data-width=1250}
-------------------------------------------
```{r warning text, echo=FALSE}
renderText({
  
  
  if(length(input$states)==0){
    return("Please select at least 1 state")
  }
 if(length(input$states)>5){
   return("Please select 5 states or less")
  }
  
  
})

```

### Vaccination Trends
```{r rendering vaccination plot, echo=FALSE}
  renderPlotly({
    
 vt2 = gsub(" ", "_", as.character(input$vaccine_trend_2))
 
    
  if(length(input$states)>0|length(input$states)<=5){
      graph_data=vaccines%>%filter(location%in%input$states)
    
    plot = ggplot(data = graph_data, aes_string(x="date", y=vt2, fill="location")) 
    plot = plot + theme(axis.text.x=element_text(angle=45, size = 10)) + ggtitle(as.character(input$vaccine_trend_2)) +theme(legend.title=element_blank())+ylab(input$vaccine_trend_2)
     if(input$points){
      plot = plot+ geom_point(aes(color=location))
     }
    if(input$line){
      plot = plot+geom_line(aes(color=location), se=FALSE)
    }
    if(input$smooth){
      plot = plot+geom_smooth(aes(color=location), se=FALSE)
    }
  }
    
  
    if(length(input$states)==0|length(input$states)>5){
       graph_data=vaccines
       plot = ggplot(data = graph_data, aes_string(x="date", y=vt2)) +ggtitle(as.character(input$vaccine_trend_2)) +theme(legend.title=element_blank())+ylab(input$vaccine_trend_2)
    }

    
 ggplotly(plot)
 
})
```

### Google Search Trend
```{r rendering google trends plot, echo=FALSE, message=FALSE}

renderPlotly({
  
  if(input$google_trends_2=="covid"){
    googtrend = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Google%20Trends%20Data/covid%20data.csv")
  }
  else if(input$google_trends_2=="vaccine"){
    googtrend = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Google%20Trends%20Data/vaccine%20data.csv")
  }
   else if(input$google_trends_2=="vaccine near me"){
    googtrend = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Google%20Trends%20Data/vaccine%20near%20me%20data.csv")
   }
   else if(input$google_trends_2=="mask"){
    googtrend = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Google%20Trends%20Data/mask%20data.csv")
   }
    else if(input$google_trends_2=="social distancing"){
    googtrend = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Google%20Trends%20Data/social%20distancing%20data.csv")
   }
   else if(input$google_trends_2=="qanon"){
    googtrend = read_csv("https://raw.githubusercontent.com/nanand7/DS-Project-2021/main/Google%20Trends%20Data/qanon%20data.csv")
   }
  
   googtrend$hits = as.numeric(googtrend$hits)

   if(length(input$states)!=0|length(input$states)<=5){
      graph_data_goog=googtrend%>%filter(geo%in%input$states)
    
    plot2 = ggplot(data = graph_data_goog, aes(x=date, y=hits, fill=geo)) 
    plot2 = plot2 + theme(axis.text.x=element_text(angle=45, size = 10)) + ggtitle(as.character(input$google_trends_2)) +theme(legend.title=element_blank())
   if(input$points){
      plot2 = plot2+ geom_point(aes(color=geo))
   }
    if(input$line){
      plot2 = plot2+geom_line(aes(color=geo), se=FALSE)
    }
   if(input$smooth){
      plot2 = plot2+geom_smooth(aes(color=geo), se=FALSE)
    }
   
   }

   if(length(input$states)==0|length(input$states)>5){
       graph_data_goog=googtrend
      plot2 = ggplot(data = graph_data_goog, aes(x=date, y=hits)) + ggtitle(as.character(input$google_trends_2)) +theme(legend.title=element_blank())
      

    }

 ggplotly(plot2)



})
```


Column {data-width=700}
-------------------------------------------

### Model Details
```{r, echo=FALSE}
renderTable({

  library(data.table)
   vt2 = c(gsub(" ", "_", as.character(input$vaccine_trend_2)))
 if(length(input$states)>0&length(input$states)<=5){
  display = model_dat %>% 
  filter(outcome%in%vt2)%>%
  filter(term%in%input$google_trends_2)%>%
  filter(state%in%input$states)%>%
  filter(lagd==-3|lagd==-7|lagd==-14)%>%
  select("state", "term", "lagd", "croscor")%>%
  rename(
    "State" = state,
    "Google Trend" = term,
    "Cross correlation" = croscor,
    "Days lagged" = lagd)
  
    return(setDT(display))
 }
   
else{
  display = model_dat %>% 
  filter(outcome=="")%>%
  select("state", "term", "croscor")%>%
  rename(
    "State" = state,
    "Google Trend" = term,
    "Cross correlation" = croscor,
    "Days lagged" = lagd)
  
  return(setDT(display))
  
}

})
```

Web App Details 
======================
### App Details 
Write details about final app here
Vaccination data from: Our World in Data - https://github.com/owid/covid-19-data/tree/master/public/data/vaccinations 
Cases and deaths data from: COVID-19 Data Repository by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University - https://github.com/CSSEGISandData/COVID-19/tree/master/csse_covid_19_data/csse_covid_19_time_series 
